Revision Plan for SIGCOMM'24 Paper \#293

### 2024-06-05 response.tex

%\noindent\textcolor{blue}{\textbf{Response C.1:}
%Thanks for the reviewer’s comments. 
%Indeed, in section 2.3, we mention that \emph{DCTCP marks ECN at the switch for arriving packets if queue occupancy exceeds a threshold K, and the sender cuts the window based on the fraction of ECN marked ACKs. So, when there are multiple concurrent flows, DCTCP may mark ECN for packets from many flows, which may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized.}
%To show this point, We run ns-3 simulations with two senders and one receiver sharing the bottleneck. 
%We sample the bottleneck link utilization every 100us for 10ms when DCTCP enters a steady state.
%We plot the results in Figure 1, showing that nearly half of the bandwidth is underutilized.
%}

{\it \paragraph{C.2: Reviewer Comment:} Figure 13 doesn’t add up by itself. RC3 has the highest average FCT for small and large flows. However, its overall average is not the highest. Given that large and small flows account for 13\% and 87\% respectively, the overall average should be around 0.13 * 39.63 + 0.87 * 0.77 = 5.8? Or am I missing something?}

\noindent\textcolor{blue}{\textbf{Response C.2:}
Thanks for the reviewer’s very good comments. 
This may be a typing error when drawing the figure.
We will revise it accordingly.
%After we checked the experimental data we found that the results were error due to our input errors.
%We will revise all affected parts of the entire article.
%After carefully checking our data processing code, we found that under Datamining workloads, RC3 would result in a few flows not completing due to many packet losses.
%Our code incorrectly used the program runtime as the flow completion time when calculating the overall average FCT, resulting in the actual computed result being larger.
%We will fix the bug and update the correct result.
}

\noindent\textcolor{red}{\textbf{Specific modification: }
We have corrected this typo. Please see Fig. 13(a) on page 12 in our revised paper.
}

{\it \paragraph{C.3: Reviewer Comment:} Page 12, can you give an intuition why limiting RC3’s low priority queue doesn’t help? It kind of contradicts the argument that aggressive low priority packets hinder high-priority packets being a problem if the high-priority queue has enough buffers?}

\noindent\textcolor{blue}{\textbf{Response C.3:}
Thanks for the reviewer's comments. 
We will add more intuitive reasons in Section 6.2 to show this point.
%Although limiting the RC3 low-priority queue can prevent the LCP from sending too many opportunity packets, the following reasons still lead to low performance.
%First, during the slow-start phase of the flow, limiting the buffer LCP could use will leave a large amount of bandwidth underutilized.
%Second, RC3 keeps the LCP open instead of intermittent initialization as PPT, which causes more severe congestion during traffic bursts.
%Last but not least, RC3's lack of using in-network priority causes small flow packets to be queued after LCP packets, increasing small flow latency.
%We will add the above analyses to our paper.
}

\noindent\textcolor{red}{\textbf{Specific modification: }
We have added more intuitive reasons about this point. Please see the blue text on Column 1, Page 15 in our revised paper.
}

\subsection{Reviewer \#293D}

{\it \paragraph{D.1: Reviewer Comment:}Overall, given the recent research on protocols that are both (a) simpler than DCTCP to deploy and (b) deliver better performance than it, it is unclear to me why one would want to have an "add-on" system (with its own additional complexities) to help it perform better.}

\noindent\textcolor{blue}{\textbf{Response D.1}
Thanks for the reviewer's good comments.
In fact, DCTCP is widely deployed in production and used as the default congestion control algorithm in linux kernel for many years.
Therefore, DCTCP has fewer barriers to adoption and a broader reach compared to other transport protocols.
Moreover, through our design and experiments, we have already demonstrated that we can achieve good performance by utilizing the spare bandwidth of DCTCP, while retaining the compatibility with legacy TCP/IP network stacks.
These factors motivate us to design an add-on system on DCTCP.
}

\noindent\textcolor{red}{\textbf{Specific modification: }
As we have already explained this motivation in section 2.3, we will not add further explanation in our revised paper.
}

{\it \paragraph{D.2: Reviewer Comment:}Related work: The paper misses the recent delay-based congestion control algorithms such as Timely and Swift both in the qualitative discussions (e.g., Table 1) and in the quantitative comparisons in the evaluation section. Appendix C provides some data but needs some clarification. What exactly is "a delay-based transport (conceptually equivalent to Swift)." What is the actual algorithm?}

\noindent\textcolor{blue}{\textbf{Response D.2}
Thanks for the comments. The variant actually doesn't include Swift's component that handles endpoint congestion. 
}

\noindent\textcolor{red}{\textbf{Specific modification: }
We have added a new footnote 7 on Column 1, Page 12 in our revised paper to clarify the exact algorithm the reviewer mentioned.
}

{\it \paragraph{D.3: Reviewer Comment:} I'm not sure if I fully understand some of the experimental results. To give an example, why is Homa's performance so poor for the testbed incast experiment? You mention that PPT is effective because it can recover quickly but why can't Homa?}

\noindent\textcolor{blue}{\textbf{Response D.3:}
Thanks for the reviewer's comments.
Note that the original Homa SIGCOMM'18 paper does not provide implementation code, so we use its Homa-Linux implementation (which is published in ATC'21).
However, Homa-Linux over-tunes the entire TCP/IP network stack and suffers from several implementation issues (as we have already discussed in Section 6.1.1).
%As mentioned in Section 6.1.2, Homa-Linux sends BDP-sized unscheduled packets for each arriving flow, and excessive opportunity packets cause heavier congestion in incast scenarios.
%Furthermore, Homa-Linux is connectionless, so packet loss recovery is achieved through retransmission after timeout.
%Large packet loss in Incast scenarios further impairs its performance.
%We will add more detailed analyses in the paper.
}

\noindent\textcolor{red}{\textbf{Specific modification: }
According to the response above, we will not add further explanation in our revised paper.
}

\subsection{Reviewer \#293E}

{\it \paragraph{E.1: Reviewer Comment:} In production systems, priority queues are scarce resource. Using only two HW queues for one application will be a luxury. How does PTP perform with 2 prio queues (one high, one low) compared to existing production solutions like Swift, HPCC, DCTCP?}

\noindent\textcolor{blue}{\textbf{Response E.1:}
Thanks for the reviewer’s comments. 
Actually, in our paper, we have already evaluated the performance of PPT using only two queues. Please see Fig.~19 for more details.
Besides, we have also already compared PPT with HPCC. Please see Fig. 16.
}

\noindent\textcolor{red}{\textbf{Specific modification: }
According to the above response, we will not add further explanation in the revised paper.
}

{\it \paragraph{E.2: Reviewer Comment:} Even the 'large-scale' simulations cover only 144 servers w/ 40~100G as core link speeds. This resembles DC topology of more a decade ago. With the trend of AI clusters growing to have 10s of Ks of GPUs, I believe at least 2K or more endpoints must be simulated to see the real impact on shallow switch.}

\noindent\textcolor{blue}{\textbf{Response E.2}
Thanks for the reviewer’s comments. 
Our current topology is commonly used in datacenter networking community.
Simulation with 2K-node scale takes significant time, which may miss the camera-ready deadline.
%We will add a large-scale simulation experiment with 2k nodes to the appendix.
}

\noindent\textcolor{red}{\textbf{Specific modification: }
We plan to do it in the future.
}

{\it \paragraph{E.3: Reviewer Comment:} Fairness and TCP friendliness discussion are missing: tail FCT of large flows can tell the impact on fairness but is completely missing.}

\noindent\textcolor{blue}{\textbf{Response E.2}
PPT's HCP is exactly DCTCP. So, PPT is essentially a TCP-friendly design.
Regarding the fairness issue, frankly speaking, we have not taken it into account.
But this may not matter too much.
This is because in PPT's design, only the congestion windows after the congestion-avoidance phase are considered for computing $W_{max}$.
}

\noindent\textcolor{red}{\textbf{Specific modification: }
We have added a footnote 3 on Column 1, Page 6 in our revised paper to discuss the fairness issue.
}

%\noindent\textcolor{red}{\textbf{Specific modification: }
%We have added an analysis in the footnote on page 6.
%}

%\begin{spacing}{-1.0}
%\bibliographystyle{IEEEtran}
%\vspace{-0.1in}
%\bibliography{bibfile}
%\end{spacing}
\end{document}

##########################################################################################################
